A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-11 manuscript.Rmd
update simulation, add as make dependency
cite worcs for data #54

If any of these commands find that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated for each project.

@@

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder. The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions.<!--AP this is from your thesis - can you please add citations as to which practices and conventions these are?-->
To create one, click on:

@@

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recommend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository.
In practice, however, there are various reasons, which may prohibit you from making your data available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.

>>>>

If these commands detect that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated per project.

@@

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
To create one, click on:

@@

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manuel` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manuel`.
We recomend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

@@

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the availability of code and data.
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data is also stored in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs].
In practice, however, there are various reasons, which may prohibit you from making your data available, for example legal or regulatory or privacy concerns.
You may find yourself in a situation where you can make the data only available on request.
A major threat to reproducibility is that the data has changed in the meantime or multiple versions are circulating and it is not exactly clear what version was used originally.
To at least check that the data was not changed, we suggest to provide a so called "hash", which is a cryptographic fingerprint.
If the data changes, so does its fingerprint or hash.
The user can therefore compare if the data they have received is the same that was used in the original publication, as long as the original publication does contain the hash of the data.
